Supplementary materials

### 2018-02-23 publication/supp_info.Rmd
Make abundance plot smaller

```{r fig-abundance-logtransformed-or-not, fig.height = 3, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
loadd(plant_rel_abu, sites)

>>>>

```{r fig-abundance-logtransformed-or-not, fig.height = 2.5, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
loadd(plant_rel_abu, sites)
